Bias no more: A practical guide to latent group-mean centering in longitudinal and other hierarchical bayesian models

### 2022-12-07 ms.Rmd
Set document options

```{r setup, include = FALSE}
library(papaja)
library(posterior)
library(scales)
library(ggdist)
library(brms)
library(tidyverse)

>>>>

```{r setup, include = FALSE}
library(papaja)
library(posterior)
library(knitr)
library(scales)
library(ggdist)
library(brms)
library(tidyverse)

# Document options
opts_chunk$set(
  cache = TRUE,
  echo = FALSE
)
